Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-02-02 manuscript/cpcrw_manuscript.Rmd
Methods - removals and exclusions

@@

@@

**Statistical analysis**

Outlier exclusion based on 3.2 mean absolute deviations {Davies, 1993 #3138} from treatment and temperature mean. We excluded X of Y (Z%) of the summarized samples for this reason.

>>>>

```{r, echo=FALSE}
library(dplyr)
```

@@

Alaska forests under particular stress - browning {Ju, 2016 #4320}

@@

**Data and statistical analysis**

We measured the rise in GHG concentrations from its minimum value (in the first 10 seconds of measurement after the analyzer was sealed to the soil core) to its maximum (in the first 45 seconds), considering this as the flux rate in ppm s^-1^ (CO2) or ppb s^-1^ (CH4). This value was calculated for each sample, i.e. each individual core measurement throughout the 100-day incubation.

```{r, echo=FALSE}
# compute outlier and exclusion numbers
sdn <- readLines("../outputs/summarydata.csv") %>% length
sdcn <- readLines("../outputs/summarydata_clean.csv") %>% length
en <- readLines("../outputs/2.5-remove/excluded_data.csv") %>% length
rn <- readLines("../outputs/2.5-remove/removed_data.csv") %>% length
```

Anomalous data were excluded based on their being more than 3.2 mean absolute deviations {Davies, 1993 #3138} from the treatment and temperature mean. We excluded `r en` of `r sdn` (`r round(en/sdn*100)`%) of the summarized samples for this reason. Other data (`r rn` of `r sdn`, `r round(rn/sdn*100)`%) were removed because of known instrument problems, e.g. the analyzer was left running after leaving a chamber. The final number of valid flux samples from the 100-day incubation was `r sdcn`.

* joined with mass data
* flux computation
* stats
